Learning \strips\ action models with classical planning

### 2017-11-13 doc/icaps-18/strips-learning.tex
Modifications in the last section of the paper

The approach for learning planing models that most likely works with the least information possible is {\sf LOCM} ~\cite{cresswell2013acquiring}, where the only required input are the example training plans without the need for providing the initial and goal state information. {\sf LOCM} exploits assumptions about the kind of domain model it has to generate. Particularly, it assumes a domain consists of a collection of objects (called \emph{sorts}) where each object has a defined set of states that can be captured by a parameterized Finite State Machine (FSM). The induction of FSM draws upon assumptions like the continuity of object transitions or the association of parameters between consecutive actions in the training sequence. The intuitive assumptions of {\sf LOCM} yield a learning model heavily reliant on the kind of domain structure and not capable of properly deriving domain theories in which the state of a sort is subject to different state machines. This limitation is later overcome by {\sf LOCM2} by forming separate state machines for a sort, each containing a subset of the full transition set for the sort~\cite{cresswell2011generalised}. The last contribution of the {\sf LOCM} family, {\sf LOP} ({\sf LOCM} with Optimized Plans ~\cite{GregoryC16}), addresses the problem of inducing static predicates in action models by identifying the set of minimal static relations associated to an operator. Because {\sf LOCM} models induce similar models for domains with similar structure (e.g. Blocksworld and Freecell), they face problems at identifying models that do not have static relations (Blocksworld) and those that do have static predicates (Freecell). In order to mitigate this drawback, {\sf LOP} applies a post-processing step after the {\sf LOCM} analysis which requires additional information about the plans, namely a set of optimal plans to be used in the learning phase.

>>>>

{\sf LOCM} only requires the example training plas as input without need for providing information about predicates or states~\cite{cresswell2013acquiring}. This makes {\sf LOCM} be most likely the learning approach that works with the least information possible. The lack of available information is addressed by LOCM by exploting assumptions about the kind of domain model it has to generate. Particularly, it assumes a domain consists of a collection of objects (sorts) whose defined set of states can be captured by a parameterized Finite State Machine (FSM). The intuitive assumptions of {\sf LOCM}
%, like the continuity of object transitions or the association of parameters between consecutive actions in the training sequence, 
yield a learning model heavily reliant on the kind of domain structure. The inability of {\sf LOCM} to properly derive domain theories where the state of a sort is subject to different FSMs is later overcome by {\sf LOCM2} by forming separate FSMs, each containing a subset of the full transition set for the sort~\cite{cresswell2011generalised}. {\sf LOP} ({\sf LOCM} with Optimized Plans ~\cite{gregory2015domain}), the last contribution of the {\sf LOCM} family, addresses the problem of inducing static predicates. Because {\sf LOCM} approaches induce similar models for domains with similar structures, they face problems at generating models for domains that are only distinguished by whether or not they contain static relations (e.g. {\em blocksworld} and {\em freecell}). In order to mitigate this drawback, {\sf LOP} applies a post-processing step after the {\sf LOCM} analysis which requires additional information about the plans, namely a set of optimal plans to be used in the learning phase.

Compiling the learning task into a a classical planning task is a general and flexible solution as it allows to accommodate different amounts of input knowledge. This scheme opens up a path for solving further tasks other than learning action models or plan validation -- when a fully specified action model $\Xi$ is given. Thus, by replacing the learning examples of $\Pi$ by sequences of states (observations), noisy or missing fluents could be introduced in the states, and so the learning task $\Lambda=\tup{\Psi,\Sigma,\mathcal{O},\Xi}$, where $\mathcal{O}$ is the noisy or partial observations, would amount to a plan recognition task where the domain theory is given~\cite{SohrabiRU16}. Furthermore, the compilation scheme can be extended to learn other type of generative models that comprise partially-specified solution plans like HTN models or full-specified solutions like FSM or behaviour trees.
